Курсовая работа по теме \\ \Huge{«Методы оптимизации»}

### 2008-12-17 simplex-method.tkz.tex
Adjusted axis limits

\begin{figure}[!thb]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
      x=1.5cm, y=1.5cm,
      xlabel=$x_1$,
      ylabel=$x_2$,
      xtick={1, 2, 3, 4, 5, 6},
      ytick={1, 3, 4, 5},
      xmin=-2, ymin=-1,
      xmax=7, ymax=6,
      axis x line=center,
      axis y line=center,
      pattern color=gray]

@@

      % Boundaries
      \draw[thick] (axis cs:-1, 1.25)--(axis cs:4, 5)
      node [sloped,above,pos=0.85] {$-3x_1+4x_2 = 8$};
      \draw[thick] (axis cs:1.5, 4.0833)--(axis cs:5.5, -0.5833)
      node [sloped,above,pos=0.5] {\contour{white}{$7x_1+6x_2=35$}};

>>>>

\begin{figure}[!thb]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
      x=1.5cm, y=1.5cm,
      xlabel=$x_1$,
      ylabel=$x_2$,
      xtick={1, 2, 3, 4, 5, 6},
      ytick={1, 3, 4, 5},
      xmin=-1, ymin=-1,
      xmax=7, ymax=6,
      axis x line=center,
      axis y line=center,
      pattern color=gray]

@@

      % Boundaries
      \draw[thick] (axis cs:-0.5, 1.625)--(axis cs:4, 5)
      node [sloped,above,pos=0.85] {$-3x_1+4x_2 = 8$};
      \draw[thick] (axis cs:1.5, 4.0833)--(axis cs:5.5, -0.5833)
      node [sloped,above,pos=0.5] {\contour{white}{$7x_1+6x_2=35$}};
